---
title: "p8105_hw1_jy2947"
author: "Jiawei Ye"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```


This is the first homework of P8105.

## Problem 1

The following code chunk creates the data frame as required. It also calculates the mean of each variable in the dataframe.  
```{r create_uniform_distribution}
dataframe = tibble(
  sample = runif(10, min = 0, max = 5),
  morethan2 = c(sample[1:10] > 2),
  p1_cha = c('JohnyDepp','AlanRickman','Eddie','Benedict','Watson','f','g','h','i','SeverusSnape'),
  p1_fac = factor(c('A','A','C','C','A','B','B','E','E','A'))
)
mean(dataframe$sample)
mean(dataframe$morethan2)
mean(dataframe$p1_cha)
mean(dataframe$p1_fac)
```
The mean of `sample` and `morethan2` works, `p1_cha` and `p1_fac` do not work and the outputs are `NA`. Obviously you cannot calculate the mean of characters and factors. I think elements in `morethan2` are treated as zeros and ones so R can calculate its mean. 


The following code chunk tries to convert logical/character/factor vectors to numerical vectors.
```{r convert_to_num, eval = FALSE}
as.numeric(dataframe$morethan2)
as.numeric(dataframe$p1_cha)
as.numeric(dataframe$p1_fac)
```